model

### 2024-03-14 analysis/gafo-cc-model.Rmd
finalize model comparison

```{r, message=FALSE, warning=F}
# mexico_model_comparison <- rbindlist(
#   list(
#      fread("../model/output/mexico_model_comparison_chain1.csv"),
#      fread("../model/output/mexico_model_comparison_chain2.csv"),
#      fread("../model/output/mexico_model_comparison_chain3.csv"),
#      fread("../model/output/mexico_model_comparison_chain4.csv"),
#      fread("../model/output/mexico_model_comparison_chain5.csv"),
#      fread("../model/output/mexico_model_comparison_chain6.csv")
#     ), use.names=TRUE)%>%
#   group_by(chain, iteration, model)%>%
#   summarise(like = sum(loglike))%>%
#   mutate(community = "mexico")%>%
#   saveRDS("../model/output/mexico_model_comparison.rds")

 mexico_model_comparison <- readRDS("../model/output/mexico_model_comparison.rds")
```

@@

```{r, message=FALSE, warning=F}
# nigeria_model_comparison <- rbindlist(
#   list(
#      fread("../model/output/akure_model_comparison_chain1.csv"),
#      fread("../model/output/akure_model_comparison_chain2.csv"),
#      fread("../model/output/akure_model_comparison_chain3.csv"),
#      fread("../model/output/akure_model_comparison_chain4.csv"),
#      fread("../model/output/akure_model_comparison_chain5.csv"),
#      fread("../model/output/akure_model_comparison_chain6.csv")
#     ), use.names=TRUE)%>%
#   group_by(chain, iteration, model)%>%
#   summarise(like = sum(loglike))%>%
#   mutate(community = "nigeria")%>%
#   saveRDS("../model/output/nigeria_model_comparison.rds")

@@

```{r, message=FALSE, warning=F}
# bandongo_model_comparison <- rbindlist(
#   list(
#     fread("../model/output/bandongo_model_comparison_chain1.csv"),
#     fread("../model/output/bandongo_model_comparison_chain2.csv"),
#     fread("../model/output/bandongo_model_comparison_chain3.csv"),
#     fread("../model/output/bandongo_model_comparison_chain4.csv"),
#     fread("../model/output/bandongo_model_comparison_chain5.csv"),
#     fread("../model/output/bandongo_model_comparison_chain6.csv")
#   ), use.names=TRUE)%>%
#   group_by(chain, iteration, model)%>%
#   summarise(like = sum(loglike))%>%
#   mutate(community = "bandongo")%>%
#   saveRDS("../model/output/bandongo_model_comparison.rds")

bandongo_model_comparison <- readRDS("../model/output/bandongo_model_comparison.rds")
```

@@

```{r, message=FALSE, warning=F}
khwe_model_comparison <- rbindlist(
  list(
    fread("../model/output/khwe_model_comparison_chain1.csv"),
    fread("../model/output/khwe_model_comparison_chain2.csv"),
    fread("../model/output/khwe_model_comparison_chain3.csv"),
    fread("../model/output/khwe_model_comparison_chain4.csv"),
    fread("../model/output/khwe_model_comparison_chain5.csv"),
    fread("../model/output/khwe_model_comparison_chain6.csv")
  ), use.names=TRUE)%>%
  group_by(chain, iteration, model)%>%
  summarise(like = sum(loglike))%>%
  mutate(community = "khwe")%>%
  saveRDS("../model/output/khwe_model_comparison.rds")

@@

```{r, message=FALSE, warning=F}
plymouth_model_comparison <- rbindlist(
  list(
    fread("../model/output/plymouth_model_comparison_chain1.csv"),
    fread("../model/output/plymouth_model_comparison_chain2.csv"),
    fread("../model/output/plymouth_model_comparison_chain3.csv"),
    fread("../model/output/plymouth_model_comparison_chain4.csv"),
    fread("../model/output/plymouth_model_comparison_chain5.csv"),
    fread("../model/output/plymouth_model_comparison_chain6.csv")
  ), use.names=TRUE)%>%
  group_by(chain, iteration, model)%>%
  summarise(like = sum(loglike))%>%
  mutate(community = "plymouth")%>%
  saveRDS("../model/output/plymouth_model_comparison.rds")

@@

```{r, message=FALSE, warning=F}
stanford_model_comparison <- rbindlist(
  list(
    fread("../model/output/stanford_model_comparison_chain1.csv"),
    fread("../model/output/stanford_model_comparison_chain2.csv"),
    fread("../model/output/stanford_model_comparison_chain3.csv"),
    fread("../model/output/stanford_model_comparison_chain4.csv"),
    fread("../model/output/stanford_model_comparison_chain5.csv"),
    fread("../model/output/stanford_model_comparison_chain6.csv")
  ), use.names=TRUE)%>%
  group_by(chain, iteration, model)%>%
  summarise(like = sum(loglike))%>%
  mutate(community = "stanford")%>%
  saveRDS("../model/output/stanford_model_comparison.rds")

@@

```{r, message=FALSE, warning=F}
turkey_model_comparison <- rbindlist(
  list(
    fread("../model/output/turkey_model_comparison_chain1.csv"),
    fread("../model/output/turkey_model_comparison_chain2.csv"),
    fread("../model/output/turkey_model_comparison_chain3.csv"),
    fread("../model/output/turkey_model_comparison_chain4.csv"),
    fread("../model/output/turkey_model_comparison_chain5.csv"),
    fread("../model/output/turkey_model_comparison_chain6.csv")
  ), use.names=TRUE)%>%
  group_by(chain, iteration, model)%>%
  summarise(like = sum(loglike))%>%
  mutate(community = "turkey")%>%
  saveRDS("../model/output/turkey_model_comparison.rds")

@@

@@

```{r, message=FALSE, warning=F}
windhoek_model_comparison <- rbindlist(
  list(
    fread("../model/output/windhoek_model_comparison_chain1.csv"),
    fread("../model/output/windhoek_model_comparison_chain2.csv"),
    fread("../model/output/windhoek_model_comparison_chain3.csv"),
    fread("../model/output/windhoek_model_comparison_chain4.csv"),
    fread("../model/output/windhoek_model_comparison_chain5.csv"),
    fread("../model/output/windhoek_model_comparison_chain6.csv")
  ), use.names=TRUE)%>%
  group_by(chain, iteration, model)%>%
  summarise(like = sum(loglike))%>%
  mutate(community = "windhoek")%>%
  saveRDS("../model/output/windhoek_model_comparison.rds")

@@

```{r}
bf_comparison <- bind_rows(
  haillom_model_comparison,
  chimfunshi_model_comparison,
  mexico_model_comparison,
  india_model_comparison,
  nigeria_model_comparison,
  china_model_comparison,
  argentina_model_comparison,
  leipzig_model_comparison,
  auckland_model_comparison,
  bandongo_model_comparison,
  bayaka_model_comparison,
  khwe_model_comparison,
  plymouth_model_comparison,
  stanford_model_comparison,
  turkey_model_comparison,
  windhoek_model_comparison
) %>%
  group_by(community, model)%>%
  summarise(margllh = logSumExp(like))%>%
  pivot_wider(names_from = model, values_from = margllh)%>%
  summarise(bf_inf_center = inf - center, 
            bf_inf_guess = inf - guess)

>>>>

```{r, message=FALSE, warning=F}
# mexico_model_comparison <- rbindlist(
#   list(
#      fread("../model/output/mexico_model_comparison_chain1.csv"),
#      fread("../model/output/mexico_model_comparison_chain2.csv"),
#      fread("../model/output/mexico_model_comparison_chain3.csv"),
#      fread("../model/output/mexico_model_comparison_chain4.csv"),
#      fread("../model/output/mexico_model_comparison_chain5.csv"),
#      fread("../model/output/mexico_model_comparison_chain6.csv")
#     ), use.names=TRUE)%>%
#   group_by(chain, iteration, model)%>%
#   summarise(like = sum(loglike))%>%
#   mutate(community = "mexico")%>%
#   saveRDS("../model/output/mexico_model_comparison.rds")
# 
#  mexico_model_comparison <- readRDS("../model/output/mexico_model_comparison.rds")
```

@@

```{r, message=FALSE, warning=F}
# nigeria_model_comparison <- rbindlist(
#   list(
#      fread("../model/output/akure_model_comparison_chain1.csv"),
#      fread("../model/output/akure_model_comparison_chain2.csv"),
#      fread("../model/output/akure_model_comparison_chain3.csv"),
#      fread("../model/output/akure_model_comparison_chain4.csv"),
#      fread("../model/output/akure_model_comparison_chain52.csv"),
#      fread("../model/output/akure_model_comparison_chain6.csv")
#     ), use.names=TRUE)%>%
#   group_by(chain, iteration, model)%>%
#   summarise(like = sum(loglike))%>%
#   mutate(community = "nigeria")%>%
#   saveRDS("../model/output/nigeria_model_comparison.rds")

@@

```{r, message=FALSE, warning=F}
# bandongo_model_comparison <- rbindlist(
#   list(
#     fread("../model/output/bandongo_model_comparison_chain1.csv"),
#     fread("../model/output/bandongo_model_comparison_chain2.csv"),
#     fread("../model/output/bandongo_model_comparison_chain3.csv"),
#     fread("../model/output/bandongo_model_comparison_chain4.csv"),
#     fread("../model/output/bandongo_model_comparison_chain5.csv"),
#     fread("../model/output/bandongo_model_comparison_chain6.csv")
#   ), use.names=TRUE)%>%
#   group_by(chain, iteration, model)%>%
#   summarise(like = sum(loglike))%>%
#   mutate(community = "bandongo")%>%
#   saveRDS("../model/output/bandongo_model_comparison.rds")
# 
bandongo_model_comparison <- readRDS("../model/output/bandongo_model_comparison.rds")
```

@@

```{r, message=FALSE, warning=F}
# khwe_model_comparison <- rbindlist(
#   list(
#     fread("../model/output/khwe_model_comparison_chain1.csv"),
#     fread("../model/output/khwe_model_comparison_chain2.csv"),
#     fread("../model/output/khwe_model_comparison_chain3.csv"),
#     fread("../model/output/khwe_model_comparison_chain4.csv"),
#     fread("../model/output/khwe_model_comparison_chain5.csv"),
#     fread("../model/output/khwe_model_comparison_chain6.csv")
#   ), use.names=TRUE)%>%
#   group_by(chain, iteration, model)%>%
#   summarise(like = sum(loglike))%>%
#   mutate(community = "khwe")%>%
#   saveRDS("../model/output/khwe_model_comparison.rds")

@@

```{r, message=FALSE, warning=F}
# plymouth_model_comparison <- rbindlist(
#   list(
#     fread("../model/output/plymouth_model_comparison_chain1.csv"),
#     fread("../model/output/plymouth_model_comparison_chain2.csv"),
#     fread("../model/output/plymouth_model_comparison_chain3.csv"),
#     fread("../model/output/plymouth_model_comparison_chain4.csv"),
#     fread("../model/output/plymouth_model_comparison_chain5.csv"),
#     fread("../model/output/plymouth_model_comparison_chain6.csv")
#   ), use.names=TRUE)%>%
#   group_by(chain, iteration, model)%>%
#   summarise(like = sum(loglike))%>%
#   mutate(community = "plymouth")%>%
#   saveRDS("../model/output/plymouth_model_comparison.rds")

@@

```{r, message=FALSE, warning=F}
# stanford_model_comparison <- rbindlist(
#   list(
#     fread("../model/output/stanford_model_comparison_chain1.csv"),
#     fread("../model/output/stanford_model_comparison_chain2.csv"),
#     fread("../model/output/stanford_model_comparison_chain3.csv"),
#     fread("../model/output/stanford_model_comparison_chain4.csv"),
#     fread("../model/output/stanford_model_comparison_chain5.csv"),
#     fread("../model/output/stanford_model_comparison_chain6.csv")
#   ), use.names=TRUE)%>%
#   group_by(chain, iteration, model)%>%
#   summarise(like = sum(loglike))%>%
#   mutate(community = "stanford")%>%
#   saveRDS("../model/output/stanford_model_comparison.rds")

@@

```{r, message=FALSE, warning=F}
# turkey_model_comparison <- rbindlist(
#   list(
#     fread("../model/output/turkey_model_comparison_chain1.csv"),
#     fread("../model/output/turkey_model_comparison_chain2.csv"),
#     fread("../model/output/turkey_model_comparison_chain3.csv"),
#     fread("../model/output/turkey_model_comparison_chain4.csv"),
#     fread("../model/output/turkey_model_comparison_chain5.csv"),
#     fread("../model/output/turkey_model_comparison_chain6.csv")
#   ), use.names=TRUE)%>%
#   group_by(chain, iteration, model)%>%
#   summarise(like = sum(loglike))%>%
#   mutate(community = "turkey")%>%
#   saveRDS("../model/output/turkey_model_comparison.rds")

@@

## uganda

```{r, message=FALSE, warning=F}
# uganda_model_comparison <- rbindlist(
#   list(
#     fread("../model/output/uganda_model_comparison_chain1.csv"),
#     fread("../model/output/uganda_model_comparison_chain2.csv"),
#     fread("../model/output/uganda_model_comparison_chain31.csv"),
#     fread("../model/output/uganda_model_comparison_chain4.csv"),
#     fread("../model/output/uganda_model_comparison_chain5.csv"),
#     fread("../model/output/uganda_model_comparison_chain61.csv")
#   ), use.names=TRUE)%>%
#   group_by(chain, iteration, model)%>%
#   summarise(like = sum(loglike))%>%
#   mutate(community = "uganda")%>%
#   saveRDS("../model/output/uganda_model_comparison.rds")

uganda_model_comparison <- readRDS("../model/output/uganda_model_comparison.rds")
```

```{r}
uganda_model_comparison%>%
  group_by(community, model,chain)%>%
  summarise(margllh = logSumExp(like), 
            n = n_distinct(iteration))%>%
  pivot_wider(names_from = model, values_from = margllh)
```

@@

```{r, message=FALSE, warning=F}
# windhoek_model_comparison <- rbindlist(
# list(
#   fread("../model/output/windhoek_model_comparison_chain1.csv"),
#   fread("../model/output/windhoek_model_comparison_chain2.csv"),
#   fread("../model/output/windhoek_model_comparison_chain3.csv"),
#   fread("../model/output/windhoek_model_comparison_chain4.csv"),
#   fread("../model/output/windhoek_model_comparison_chain5.csv"),
#   fread("../model/output/windhoek_model_comparison_chain6.csv")
# ), use.names=TRUE)%>%
# group_by(chain, iteration, model)%>%
# summarise(like = sum(loglike))%>%
# mutate(community = "windhoek")%>%
# saveRDS("../model/output/windhoek_model_comparison.rds")

@@

```{r}
bf_comparison <- bind_rows(
  haillom_model_comparison,
  chimfunshi_model_comparison,
  mexico_model_comparison,
  india_model_comparison,
  nigeria_model_comparison,
  china_model_comparison,
  argentina_model_comparison,
  leipzig_model_comparison,
  auckland_model_comparison,
  bandongo_model_comparison,
  bayaka_model_comparison,
  khwe_model_comparison,
  plymouth_model_comparison,
  stanford_model_comparison,
  turkey_model_comparison,
  windhoek_model_comparison,
  uganda_model_comparison
) %>%
  group_by(community, model)%>%
  summarise(margllh = logSumExp(like))%>%
  pivot_wider(names_from = model, values_from = margllh)%>%
  summarise(bf_inf_center = inf - center, 
            bf_inf_guess = inf - guess)
